On Adding Pattern Matching to Haskell-based Deeply Embedded Domain Specific Languages

### 2020-11-20 paper/paper.tex
Changed type-level section title
Improved description of flowchart and rewrite rule figure

\subsection{\ttt{E}, \ttt{ERep}, \ttt{ERepTy}}

@@

In the flowchart given in Figure~\ref{fig:CorePlugin}, the names in parentheses in a node refer
to the names of transformations given in the rewrite rules in Figure~\ref{fig:Rewrites}. In Figure~\ref{fig:Rewrites},
$\varepsilon$ represents an empty term (in the context of the term rewriting system used in that Figure). Calls
to \ttt{unrep :: E a -> a} are only used internally and will not exist in
the final result of the transformation.

>>>>

\subsection{The Three Major Type-Level Pieces}

@@

The plugin's control flow is described in Figure~\ref{fig:CorePlugin}. When control
flow reaches a node, the rewrite rules listed in parentheses are performed. These rewrite
rule names correspond to the rules given in Figure~\ref{fig:Rewrites}.

% In the flowchart given in Figure~\ref{fig:CorePlugin}, the names in parentheses
% in a node refer to the names of transformations given in the rewrite rules in
% Figure~\ref{fig:Rewrites}. The control flow of the plugin is described by the
% flowchart and the rewrites performed when control reaches a node is given by the list of
% rule names in parentheses in that node.

In Figure~\ref{fig:Rewrites},
$\varepsilon$ represents an empty term (in the context of the term rewriting system used in that Figure). Calls
to \ttt{unrep :: E a -> a} are only used internally and will not exist in
the final result of the transformation.
